\documentclass[%singlesided,
               doublesided,
               paper=a4,
               fontsize=10pt
              ]{my-resume}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% set geometry
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\setlength\highlightwidth{8cm}
\setlength\headerheight{2cm}            % note that margintop gets added to this value, i.e. the header bar is 5cm
\setlength\marginleft{1cm}
\setlength\marginright{\marginleft}      % needs to be 1.5 times to be actually equal. why?
\setlength\margintop{1cm}
\setlength\marginbottom{1cm}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% FONTS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\RequirePackage{fontspec}
\setmainfont{Carlito}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% COLORS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\colorlet{highlightbarcolor}{white}
\colorlet{headerbarcolor}{white}

\colorlet{headerfontcolor}{black}
\colorlet{accent}{awesome-red}
\colorlet{heading}{black}
\colorlet{emphasis}{black}
\colorlet{body}{black}
\colorlet{link-color}{black}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% set document
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

\name{Justin Napolitano}
\tagline{Open source intelligence specialist seeking role requiring analytic skill set. Experienced in \\developing work flows with Python, SAS, and SPSS. Proficient in feature extraction, \\integrating data with existing workflows, and visualizing data for peer reviewed academic papers.}
%\photo[round]{picture.jpg}{\dimexpr \headerheight-\marginbottom}   % make photo exactly match the header with margintop/marginright/marginbottom as margin

\makeheader

\highlightbar{

    \section{Contact}
    \email{justin@jnapolitano.io}
    \phone{+1-832-299-0327}
    \location{Houston, Texas}
%    \vspace{0.5em}
    \homepage{jnapolitano.io}{https://jnapolitano.io}
    \github{@justin-napolitano}{https://github.com/justin-napolitano}
    \linkedin{Justin Napolitano}{https://www.linkedin.com/in/justin-napolitano}
%    \orcid{0000-0003-0745-6521}{https://orcid.org/0000-0003-0745-6521}
%    \ads{NASA/ADS publication list}{https://ui.adsabs.harvard.edu/search/fq=\%7B!type\%3Daqp\%20v\%3D\%24fq\_database\%7D&fq\_database=database\%3A\%20astronomy&p\_=0&q=pubdate\%3A\%5B2016-01\%20TO\%209999-12\%5D\%20author\%3A(\%22Krieger\%2C\%20Nico\%22)&sort=date\%20desc\%2C\%20bibcode\%20desc}
    
    \section{Skill Tree}

    \vspace{0.5em}
    \skillsection{Programming}
    \skill{Python}{4}
    \skill{Bash}{3}
    \skill{C}{3}
    \skill{HTML/CSS}{3}
    \skill{LaTeX}{3}
    \skill{Markdown}{3}
    \skill{reStructuredText}{3} 
    \skill{Go}{2}
    \skill{Javascript}{2}
    \skill{Scala}{2}
    
    
    \vspace{0.5em}
    \skillsection{Software \& Tools}
    \skill{Jupyter}{4}
    \skill{Sphinx Documentation}{4}
    \skill{Git/GH}{3}
    \skill{Docker}{3}
    \skill{Vim}{3}
    \skill{Metasploit Framework}{3}
    \skill{Nmap}{3}
    \skill{K8s}{2}
    \skill{pyTest}{2}
%    \skill{Office}{4}
    
    \vspace{0.5em}
    \skillsection{Data Handling and Analysis}
    \skill{Pandas}{4}
    \skill{Statsmodels}{3}
    \skill{SAS}{3}
    \skill{Matplotlib}{3}
    \skill{PySpark}{3}
    \skill{Networkx}{2}
    \skill{TensorFlow/Keras}{2}
%    \skill{SPSS}{2}

    \vspace{0.5em}
    \skillsection{Database}
    \skill{JanusGraph/Gremlin}{3}
    \skill{Neo4j}{3}
    \skill{SQL}{3}
%    \skill{MongoDB}{2}

    \vspace{0.5em}
    \skillsection{Languages}
    \skill{English}{5}
    \skill{Spanish}{3}
    \skill{French}{3}
    \skill{Cantonese}{2}

%    \vspace{0.5em}
%    \skillsection{Operating Systems}
%    \skill{Linux}{4}
%    \skill{MacOS}{4}
%   \bigskip
    
%    \section{Certificates}
%    \simpleskill{Python Specialization University of Michigan/Coursera}

}
\mainbar{
    \section{Experience}
    \subsection{{Application Developer  \hfill May 2021 --- Present}}
    \subtext{BTJN, LLC \hfill Houston, Texas}
    \begin{zitemize}
        \footnotesize
        \skilling{\href{https://docs.jnapolitano.io/parts/data/web-scraping/general-purpose/docs/realtor_scraper_sheets_4/index.html}{Data Integration}}{Integrated data into client’s existing Google Sheets workflow.}
        \skilling{\href{https://docs.jnapolitano.io/parts/data/web-scraping/index.html}{Data Mining}}{Developed Python application to mine greater than 250,000 sales leads.}
        \skilling{\href{https://docs.jnapolitano.io/_modules/csv_to_neo.html\#DataPipelineFunctions}{Data Transformation}}{Transformed records to client's data format with PySpark.}
        \skilling{\href{https://docs.jnapolitano.io/_modules/csv_to_neo.html\#DataUploadFunctions}{Data Warehousing}}{Stored historical data in Neo4j warehouse.}
        \skilling{\href{https://docs.jnapolitano.io/parts/analysis/business-analysis/project-retail-sales-forecasting/code-base/SalesForcasting.html}{Sales Forecasting}}{Modeled retail sales with Statsmodels API.}
    \end{zitemize}


    \subsection{{Research Lead/Author  \hfill Jan 2017 --- Aug 2019}}
    \subtext{University of Central Florida \hfill Orlando, Florida}
    \begin{zitemize}
        \footnotesize
%        \skilling{\href{https://www.degruyter.com/document/doi/10.1515/peps-2019-0036/html?lang=en}{Article Publication}}{Published in Journal of Peace Economics, Peace Science and Public Policy.}
 %       \skilling{Peer Review}{Prepared presentation for the Peace Science Conference at the Hague.}
        \skilling{\href{https://docs.jnapolitano.io/parts/analysis/political-analysis/terrorism-conflict/project-turkish-kurdish/pdf.html}{Feature Extraction}}{Standardized feature extraction methodology from news wires.}
%        \skilling{Pipeline Management}{Warehoused data to mongoDB.}
        \skilling{\href{https://docs.jnapolitano.io/parts/analysis/political-analysis/terrorism-conflict/project-turkish-kurdish/analysis.html}{Inferential Analysis}}{Identified features correlated with increased event probability.}
        \skilling{Data Visualization}{Visualized P.O.L.E graph with Matplotlib.}
    \end{zitemize}

    \subsection{{Research Assistant \hfill Jan 2017 --- Jan 2018}}
    \subtext{University of Central Florida \hfill Orlando, Florida}
    \begin{zitemize}
        \skilling{Sentiment Analysis}{Automated sentiment analysis of sentences with Python.}
        \skilling{Data Verification}{ANOVA tested human scoring against automated scoring.}
        \skilling{Data Management}{Standardized data aggregation and storage procedures.}
    \end{zitemize}
    
    \section{Education}
    \subsection{{Bachelor Political Science \hfill Aug 2018}}
    \subtext{University of Central Florida \hfill Orlando, Florida}

    \section{Certificates}
    \subsection{{Python Specialization \hfill May 2020}}
    \subtext{University of Michigan \hfill Coursera}


    \section{Projects}
        \subsection{{\href{journal.jnapolitano.io}{Journal.Jnapolitano.io} \hfill Nov 2021 --- Present}}
        \hspace{.5em}
        {\begin{zitemize}
            \footnotesize
            \skilling{\href{https://journal.jnapolitano.io/\#articles}{Commercial Research}}{Identifying the structural factors influencing commerce.}
            \skilling{\href{https://docs.jnapolitano.io/parts/analysis/political-analysis/sup-court/project-sup-court-meta-data-graph/index.html}{Meta Data Mining}}{Extracting features from the Library of Congress API.}
            \skilling{\href{https://docs.jnapolitano.io/parts/analysis/political-analysis/sup-court/project-supcourt-tensorflow/index.html}{Tensorflow Behavioral Prediction}}{Predicting Supreme Court outcomes with TensorFlow.}
%            \skilling{\href{https://journal.jnapolitano.io/\#tutorials}{Developer Tutorials}}{Writing tutorials for developer tools and programming languages.}
%                \skilling{\href{https://journal.jnapolitano.io/\#reference}{Python Reference}}{Collecting algorithms and data structures to implement in future projects.}
            \skilling{\href{https://github.com/justin-napolitano/cv}{Static Web Site Generation}}{Creating websites with Sphinx and the Jupyter Book.}
%            \skilling{\href{docs.jnapolitano.io}{Project Documentation}}{Documenting Projects with Markdown, reStructuredText, and LaTeX.}
            \skilling{\href{https://docs.jnapolitano.io/\#python-development}{Python Tools}}{Releasing Python tools to interface with Neo4j, JanusGraph, and Google APIs.}
        \end{zitemize}
        } 
    


    \section{Publications} 
    \pubdefaultspacing
    \justinpublication
    {Turkish Kurdish Analysis Database} % Title
    {Demet Mousseau, \textbf{Justin Napolitano}, Alex Olson} % Authors
    {2019} % Year
    {Peace Economics, Peace Science and Public Policy vol 25, no. 4, pp. 36} % Journal
    {\doi{https://doi.org/10.1515/peps-2019-0036}} % ADS & arxiv links   
    
    
    \section{Competencies}
    \smallskip % additional skip because tag outlines use up space
    \tag{Legal Research}
    \tag{Python Development}
    \tag{Sales Forecasting}
    \tag{Behavioral Analysis}
%    \tag{Data Mining}
    \tag{Feature Extraction}
    \tag{Socioeconomic Research}
    \tag{Project Management}
%    \tag{ETL}
    \tag{Inferential Statistics}
    \tag{Sentiment Analysis}
    \tag{Data Visualization}
%    \tag{Penetration Testing}
%    \tag{Network Security}
    \tag{Economic Modeling}
    \tag{Ethnographic Research}
%    \tag{Graph Database}


    
}
\makebody


%\clearpage
%\pagestyle{empty}

%\section{Publications}
%\pubforcefullwidth

%Demonstrate what an \texttt{\textbackslash pagestyle\{empty\}} page looks like.
%Also show off the macros for publications that uses small icons for authors, date, journal and links.

%Achieving a good looking spacing can be tricky. For empty pagestyles where the full width is available use \texttt{\textbackslash pubforcefullwidth} to force the publoication list to take up all the available space.
%The (relative) lengths reserved for date, journal and links can be set with the parameters \texttt{\textbackslash pubdatelength}, \texttt{\textbackslash pubjournallength} and \texttt{\textbackslash publinklength} as in \texttt{\textbackslash setlength\{\textbackslash pubdatelength\}\{0.15 \textbackslash linewidth\}}.
%\bigskip

%\publication
%	{The turbulent gas structure in the centers of NGC~253 and the Milky Way} % Title
%	{\textbf{N. Krieger}, A. Bolatto, E. Koch, A. Leroy, E. Rosolowsky, F. Walter, A. Wei\ss, D. Eden, R. Levy, D. Meier, E. Mills, T. Moore, J. Ott, Y. Su, S. Veilleux} % Authors
%	{2020} % Year
%	{The Astrophysical Journal Vol. 899, Issue 2, id.158} % Journal
%	{\ADS{https://ui.adsabs.harvard.edu/abs/2020ApJ...899..158K}, \arXiv{https://arxiv.org/abs/2008.02518}} % ADS & arxiv links

%\publication
%	{The molecular ISM in the Super Star Clusters of the starburst NGC253} % Title
%	{\textbf{N. Krieger}, A. Bolatto, A. Leroy, R. Levy, E. Mills, D. Meier, S. Veilleux, F. Walter, A. Wei\ss} % Authors
%	{2020} % Year
%	{The Astrophysical Journal Vol.897, Issue 2, id.176} % Journal
%	{\ADS{https://ui.adsabs.harvard.edu/abs/2020ApJ...897..176K}, \arXiv{https://arxiv.org/abs/2006.08262}} % ADS & arxiv links

%\publication
%	{The Molecular Outflow in NGC\,253 at a Resolution of Two Parsecs} % Title
%	{\textbf{N. Krieger}, A. Bolatto, F. Walter, A. Leroy, L. Zschaechner, D. Meier, J. Ott, A. Wei\ss, E. Mills, S. Veilleux, M. Gorski} % Authors
%	{2019} % Year
%	{The Astrophysical Journal Vol.881, Issue 1, article id. 43, 20 pp} % Journal
%	{\ADS{https://ui.adsabs.harvard.edu/abs/2019ApJ...881...43K}, \arXiv{https://arxiv.org/abs/1907.00731}} % ADS & arxiv links

\end{document}
