\documentclass[letter,10pt]{article}
\usepackage{TLCresume}
\begin{document}

%====================
% EXPERIENCE A
%====================
\subsection{{Application Development  \hfill May 2021 --- Present}}
\subtext{BTJN, LLC \hfill Houston, TX}
\begin{zitemize}
    \skilling{\href{https://docs.jnapolitano.io/parts/analysis/business-analysis/project-retail-sales-forecasting/code-base/SalesForcasting.html}{Sales Forecasting}}{Modeled retail sales with SARINA, Holt-Winter, and Exponential Smoothing models with Statsmodels API.}
    \skilling{\href{https://docs.jnapolitano.io/parts/data/web-scraping/index.html}{Data Mining}}{Developed Python application to mine 10,000 unfiltered sales leads weekly.}
    \skilling{\href{https://docs.jnapolitano.io/_modules/csv_to_neo.html\#DataPipelineFunctions}{Data Transformation}}{Transformed results to client's data format with PySpark.}
    \skilling{\href{https://docs.jnapolitano.io/_modules/csv_to_neo.html\#DataUploadFunctions}{Data Warehousing}}{Stored historical data in Neo4j warehouse.}
    \skilling{\href{https://docs.jnapolitano.io/parts/data/web-scraping/general-purpose/docs/realtor_scraper_sheets_4/index.html}{Data Integration}}{Integrated data into client’s existing Google Sheets workflow.}
\end{zitemize}

%====================
% EXPERIENCE B
%====================
\subsection{{Research Lead/Author  \hfill Jan 2017 --- Aug 2019}}
\subtext{University of Central Florida \hfill Orlando, Fl}
\begin{zitemize}
    \skilling{\href{https://www.degruyter.com/document/doi/10.1515/peps-2019-0036/html?lang=en}{Article Publication}}{Led team to publish work in the Journal of Peace Economics, Peace Science and Public Policy.}
    \skilling{Peer Review}{Prepared presentation for peer review at the Peace Science Conference at the Hague.}
    \skilling{\href{https://docs.jnapolitano.io/parts/analysis/political-analysis/terrorism-conflict/project-turkish-kurdish/pdf.html}{Feature Extraction}}{Standardized feature extraction and storage methodology.}
    \skilling{Data Integration}{Warehoused data to mongoDB.}
    \skilling{\href{https://docs.jnapolitano.io/parts/analysis/political-analysis/terrorism-conflict/project-turkish-kurdish/analysis.html}{Inferential Analysis}}{Identified socio-economic features that correlate with increased probability of violence.}
    \skilling{Data Visualization}{Visually conceptualized violent event, socio-economic records, and location data with Matplotlib.}
\end{zitemize}

%====================
% EXPERIENCE C
%====================
\subsection{{Research Assistant \hfill Jan 2017 --- Jan 2018}}
\subtext{University of Central Florida \hfill Orlando, Fl}
\begin{zitemize}
    \skilling{Sentiment Analysis}{Automated sentiment analysis of sentences with Python.}
    \skilling{Data Verification}{Verified user scored sentences against automated scoring with ANOVA testing.}
    \skilling{Data Management}{Standardized data aggregation and storage procedures.}
\end{zitemize}


\end{document}